Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-10-25 manuscript/main.tex
Explicitly list the coordinates of epitope sites
Rather than providing these as a supplemental table with a single column, this
commit includes the coordinates directly in the methods.

We estimated antigenic drift for each strain using either genetic or HI data.
To estimate antigenic drift with genetic data, we implemented the cross-immunity metric originally defined by {\L}uksza and L\"assig \cite{Luksza:2014hj}.
Briefly, for each pair of strains in adjacent seasons, we counted the number of amino acid differences between the strains' HA sequences at 49 epitope sites.
We limited these pairwise comparisons to all strains sampled within the last five years from each timepoint.
For each individual strain $i$ at each timepoint $t$, we estimated that strain's ability to escape cross-immunity by summing the exponentially-scaled epitope distances between previously circulating strains and the given strain as follows.

>>>>

We estimated antigenic drift for each strain using either genetic or HI data.
To estimate antigenic drift with genetic data, we implemented the cross-immunity metric originally defined by {\L}uksza and L\"assig \cite{Luksza:2014hj}.
Briefly, for each pair of strains in adjacent seasons, we counted the number of amino acid differences between the strains' HA sequences at 49 epitope sites.
The one-based coordinates of these sites relative to the start of the HA1 segment were 50, 53, 54, 121, 122, 124, 126, 131, 133, 135, 137, 142, 143, 144, 145, 146, 155, 156, 157, 158, 159, 160, 163, 164, 172, 173, 174, 186, 188, 189, 190, 192, 193, 196, 197, 201, 207, 213, 217, 226, 227, 242, 244, 248, 275, 276, 278, 299, and 307.
We limited pairwise comparisons to all strains sampled within the last five years from each timepoint.
For each individual strain $i$ at each timepoint $t$, we estimated that strain's ability to escape cross-immunity by summing the exponentially-scaled epitope distances between previously circulating strains and the given strain as follows.
